Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-15 paper/HH4b.tex

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the electroweak
  symmetry breaking mechanism due to its sensitivity
  to the Higgs trilinear coupling.
  %
  In this work, we study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for  all relevant
  backgrounds, including the contribution from light and charm
  jet mistags that is found to be comparable
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis in a high pile-up
  environment.
  %
  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
  an overall signal significance of  $S/\sqrt{B}\simeq 4$ is obtained.
  %
  Our analysis indicates
  that the $b\bar{b}b\bar{b}$ channel
alone should allow the observation of double Higgs production
  at the High Luminosity LHC.
}

>>>>

\abstract{
  The measurement of Higgs pair production will be a cornerstone of
  the LHC program in the coming years.
  %
  Double Higgs production provides a crucial window upon the mechanism of electroweak
  symmetry breaking and has a unique sensitivity
  to the Higgs trilinear coupling.
  %
  In this work, we study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for all relevant
  backgrounds, including the contributions from light and charm
  jet mistags, which are ultimately comparable in size 
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis strategy against the
  effects of pile-up.
  %
  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
  a signal significance of  $S/\sqrt{B}\simeq 4$ is obtained,
  indicating
  that the $b\bar{b}b\bar{b}$ channel
alone could allow for the observation of double Higgs production
  at the High Luminosity LHC.
}
